### 2021-10-06 documentos/vector_space.tex
<!DOCTYPE html><html><head><title>Unable to Connect</title><style type="text/css">*{font-family: "Open Sans", sans-serif; color: rgb(101, 102, 106)}body{padding-left: 50px; background-color: #f7f7f7;}h1{font-size: 48px; font-weight: 100; letter-spacing: 0.025em}h2{font-size: 28px; font-weight: 100; letter-spacing: 0.01em}p{font-size: 13px; font-weight: 300; letter-spacing: 0.08em line-height: 1.4;}</style></head><body><h1>Error accessing site</h1><h2>Unable to Connect</h2><p>The requested site&#39;s DNS address could not be found.</p></body></html>
It's 2016; why are we using ColdFusion?!

% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vtau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
% . In components, this would read 
% \begin{equation}
% % \left(
% \sum_\vbeta
% \san_{\valpha\vbeta} \,
% % \right)
% \tau_{\vec \beta}=2^Np_{\vec\alpha}
% \label{eq:A:tau:is:p}
% \end{equation}
% where
% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
% \sa_{\alpha_N\beta_N}$. 
Using the fact that $a^{-1}=a/4$, so 
\cpnote{ojo cno factores globales, depende de la definicion de la $a$} 
% (so $A = A^{-1}/2^N$) 
\begin{equation}
A^{-1} = \frac{1}{4^N} A
\end{equation}
we can directly invert \eref{eq:lambda:is:A:tau} to obtain (in matrix form)
\begin{equation}
% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
% \tau = 
\san \lambda
=4^N \tau
\label{eq:tau:is:A:p}
\end{equation}
\cpnote{me da diferente el factor global que al resto de la banda}
which will serve as a starting point for our analysis. 
\cpnote{resaltar aca la importancia de esa ecuacion, y que se aplica
para cualquier canal diagonal de Pauli}
Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha\in \Omega$, as each member of the sum 
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 4^N,
\label{eq:sum:alpha:is:4N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. 
% }}}

Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
\eref{eq:sum:alpha:is:4N} from 
% $\sum_{\vec\beta}p_{\vec\beta}=1$ (which follows from \cpnote{ver constante de 
% normalizacion chido y ver el motivo}), and 
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=4^N$ 
(which follows from the aforementioned assumption), 
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:10}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:11}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from (\ref{eq:6}) as
well as the fact that, due 
to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.

% If this condition is fulfilled and $\tau_{\vec\alpha}=1$, then
%\begin{subequations}
%\begin{eqnarray}
%\tau_{\vec\gamma}&=&\sum_{\vec\beta}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
%\label{eq:10na}
%\\
%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
%\label{eq:10nb}
%\\
%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
%\label{eq:10nc}
%\\
%&=&\sum_{\vec\beta}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
%\label{eq:10nd}
%\\
%&=&\tau_{\vec{\gamma^\prime}}
%\label{eq:10ne}
%\end{eqnarray}
%\label{eq:10n}
%\end{subequations}
%Here the transition from (\ref{eq:10na}) to (\ref{eq:10nb}) follows from (\ref{eq:10}), from (\ref{eq:10nb}) to (\ref{eq:10nc})
%follows from (\ref{eq:11}), from (\ref{eq:10nc}) to  (\ref{eq:10nd}) follows again from (\ref{eq:10}).

Condition (\ref{eq:11}) therefore connects three multi-indinces, $\vec\alpha$, $\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies 
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature of this connection.

Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
\label{eq:12}
\end{equation}
This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that (\ref{eq:12}) may be rewritten as
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
\label{eq:13}
\end{equation}
Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
the above relation must hold individually for every index. Thus we have, 
that, for all $1\leq k\leq N$, $\gamma_k$
and $\gamma_k^\prime$ are connected by
\begin{equation}
\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
\label{eq:14}
\end{equation}
for all $0\leq\beta\leq3$. This is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha\oplus{}\gamma_k
\label{eq:15}
\end{equation}
where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure \ref{tab:1} for a detailed description.

\begin{figure}
\begin{center}
\begin{tabular}{| c | c c c c |}
\hline
$\oplus{}$ & 0 & 1& 2 & 3\\
\hline
0 & 0 & 1 & 2 & 3\\
1 & 1 & 0 & 3 & 2\\
2 & 2 & 3 & 0 & 1 \\
3 &3 & 2 & 1 & 0\\
\hline
\end{tabular}
\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that the operation
is an {\em abelian group}, in fact it corresponds to the {\em Klein group}, where the
neutral element is $0$. This is the reason for choosing an additive notation for the operation
defined in (\ref{eq:14}).
}
\label{tab:1}
\end{center}
\end{figure}

Note further that if we perform the identification
\begin{subequations}
\begin{eqnarray}
0&\to&(0,0)\label{eq:identa}\\
1&\to&(0,1)\label{eq:identb}\\
2&\to&(1,0)\label{eq:identc}\\
3&\to&(1,1)\label{eq:identd}
\end{eqnarray}
\label{eq:ident}
\end{subequations}
then the $\oplus$ operation reduces to simple vector addition in
binary arithmetic. If we therefore denote by $\overline{\alpha}$
the multi-index $\vec\alpha$ converted to a binary vector by the componentwise application of (\ref{eq:ident}),
the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
as
\begin{equation}
\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
\label{eq:17}
\end{equation}
where the addition sign here refers to ordinary binary vector addition.

From this readily follows an amusing property: the set of all multi-indices $\overline\gamma$
for which $\tau_{\overline\gamma}=1$\cpnote{I guess instead of overline, we want 
to use arrow, or this denotes something else?}, is closed under binary vector addition, in other words, it
forms a {\em vector subspace\/} of the set of all multi-indices. Indeed, let
$\overline\alpha$ and $\overline\gamma$ belong to that set. Then if 
\begin{equation}
\overline{\gamma^\prime}=\overline\alpha+\overline\gamma
\label{eq:14b}
\end{equation}
then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
and thus equal to one.

>>>>

% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vtau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
% . In components, this would read 
% \begin{equation}
% % \left(
% \sum_\vbeta
% \san_{\valpha\vbeta} \,
% % \right)
% \tau_{\vec \beta}=2^Np_{\vec\alpha}
% \label{eq:A:tau:is:p}
% \end{equation}
% where
% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
% \sa_{\alpha_N\beta_N}$. 
Using the fact that $a^{-1}=a/4$, so 
% (so $A = A^{-1}/2^N$) 
\begin{equation}
A^{-1} = \frac{1}{4^N} A
\end{equation}
we can directly invert \eref{eq:lambda:is:A:tau} to obtain 
\begin{equation}
% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
% \tau = 
% \san \lambda =2^N \tau
\sum_\vbeta \san_{\valpha \vbeta} \lambda_\vbeta =2^N \tau_\valpha
\label{eq:tau:is:A:p}
\end{equation}
which will serve as a starting point for our analysis. 
\cpnote{resaltar aca la importancia de esa ecuacion, y que se aplica
para cualquier canal diagonal de Pauli}
Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha\in \Omega$, as each member of the sum 
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. 
% }}}

Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
\eref{eq:sum:alpha:is:2N} from 
% $\sum_{\vec\beta}p_{\vec\beta}=1$ (which follows from \cpnote{ver constante de 
% normalizacion chido y ver el motivo}), and 
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$ 
(which follows from the aforementioned assumption), 
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}.

% 
% This follows from (\ref{eq:6}) as
% well as the fact that, due 
% to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.

Condition (\ref{eq:11}) therefore connects three multi-indices, $\vec\alpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection. \cpnote{I think that this paragraph can go. }

Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
as
\begin{equation}
\san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
= 
\san_{\valpha\vbeta} 
, \quad
\forall \vec\beta\in\Phi(\vec\alpha),
\label{eq:12}
\end{equation}
which can be further decomposed in 
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
  \ldots
%   \cdot\ldots\cdot 
\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
\sa_{\alpha_1\beta_1}
  \ldots
% \cdot\ldots\cdot
 \sa_{\alpha_N\beta_N}.
\label{eq:13}
\end{equation}
% Moreover, since 
% 
% 
% 
% Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% \label{eq:12}
% \end{equation}
% This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
% (\ref{eq:12}) may be rewritten as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
% \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
% \label{eq:13}
% \end{equation}
Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
the above relation must hold individually for every index\cpnote{francois, recuerdo 
que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
proque se tiene que cumplir para los indices individulaes}. Thus we have, 
that, for all $1\leq k\leq N$, $\gamma_k$
and $\gamma_k^\prime$ are connected by
\begin{equation}
\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
\label{eq:14}
\end{equation}
for all $0\leq\beta\leq3$. This is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha\oplus{}\gamma_k
\label{eq:15}
\end{equation}
where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure
\ref{tab:1} for a detailed description. \cpnote{by direct calculation I can verify 
that its true, but I see it as a coincidence. Is they ere a say to know
that \eref{eq:14} will lead to a sum?}

\begin{figure} % {{{
\begin{center}
\begin{tabular}{| c | c c c c |}
\hline
$\oplus{}$ & 0 & 1& 2 & 3\\
\hline
0 & 0 & 1 & 2 & 3\\
1 & 1 & 0 & 3 & 2\\
2 & 2 & 3 & 0 & 1 \\
3 &3 & 2 & 1 & 0\\
\hline
\end{tabular}
\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that
the operation is an {\em abelian group}, in fact it corresponds to the {\em
Klein group}, where the neutral element is $0$. This is the reason for choosing
an additive notation for the operation defined in (\ref{eq:14}).  }
\label{tab:1}
\end{center}
\end{figure} % }}}

Note further that if we perform the identification
\begin{subequations}
\begin{eqnarray}
0&\to&(0,0)\label{eq:identa}\\
1&\to&(0,1)\label{eq:identb}\\
2&\to&(1,0)\label{eq:identc}\\
3&\to&(1,1)\label{eq:identd}
\end{eqnarray}
\label{eq:ident}
\end{subequations}
then the $\oplus$ operation reduces to simple vector addition in
binary arithmetic. If we therefore denote by $\overline{\alpha}$
\cpnote{I dont think this is necesary. specially if we will write something
else}
the multi-index $\vec\alpha$ converted to a binary vector by the componentwise
application of (\ref{eq:ident}),
the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
as
\begin{equation}
\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
\label{eq:17}
\end{equation}
where the addition sign here refers to ordinary binary vector addition.

From this readily follows an amusing property: the set of all multi-indices
$\overline\gamma$ for which $\tau_{\overline\gamma}=1$, is closed under binary
vector addition, in other words, it forms a {\em vector subspace\/} of the set
of all multi-indices. Indeed, let $\overline\alpha$ and $\overline\gamma$
belong to that set. Then if 
\begin{equation}
\overline{\gamma^\prime}=\overline\alpha+\overline\gamma
\label{eq:14b}
\end{equation}
then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
and thus equal to one.
